On the number of tiles visited by a\\ line segment on a rectangular grid

### 2023-03-31 paper.tex
Issue found by the reviewer fixed
in Matlab. The paper text had not been modified yet regarding this

Given $\len \in \mathbb R^+$, let $\tiles = \funt(\len)$, and consider $i,j\geq 1$ such that $i+j-1=\tiles$. For a fixed orientation $\theta$, the segment goes from the reference tile to that with lower-left corner $(i-1,j-1)$ if and only if shifting the segment so that its second endpoint has coordinates $(i-1,j-1)$ results in the first endpoint being in the reference tile. It cannot be the case that the segment ``overshoots'' past this tile, because that would result in a number of visited tiles exceeding $\tiles$, which is the maximum.

@@

There is a range of possible values of $\theta$ for which the above condition is satisfied. This range corresponds to the part of the arc with solid line in Figure~\ref{fig: probmax_funt_odd}. For convenience, the angle $\theta$ is defined clockwise from the downward direction. For each $\theta$ in the allowed range, the valid positions for the first endpoint of the (shifted) segment are in a rectangle contained in the reference tile. The rectangle associated with an example $\theta$ is shown in the figure, shaded. The area of this rectangle is the probability $\probmax_{i-1,j-1}(\len,\theta)$ that the segment goes from the reference tile to that with lower-left corner $(i-1,j-1)$ conditioned on $\theta$. The desired probability $\probmax(\len)$ will be obtained by averaging $\probmax_{i-1,j-1}(\len, \theta)$ with respect $\theta$, summing over all $i, j \geq 1$ such that the tile with lower-left corner $(i-1, j-1)$ can be reached from the reference tile, and then using symmetry to take into account the tiles with $i \leq 0$ or $j \leq 0$.

>>>>

Given $\len \in \mathbb R^+$, let $\tiles = \funt(\len)$, and consider $i,j\geq 1$ such that $i+j-1=\tiles$. For a fixed orientation $\theta$, the segment goes from the reference tile to that with lower-left corner $(i-1,j-1)$ if and only if shifting the segment so that its second endpoint has coordinates $(i-1,j-1)$ results in the first endpoint being in the reference tile. It cannot be the case that the segment ``overshoots'' past this tile, because that would result in a number of visited tiles exceeding $\tiles$, which is the maximum by hypothesis.

@@

There is a range of possible values of $\theta$ for which the above condition is satisfied. This range corresponds to the part of the arc with solid line in Figure~\ref{fig: probmax_funt_odd}. For convenience, the angle $\theta$ is defined clockwise from the downward direction. For each $\theta$ in the allowed range, the valid positions for the first endpoint of the (shifted) segment are in a rectangle contained in the reference tile. The rectangle associated with an example $\theta$ is shown in the figure, shaded. The area of this rectangle is the probability $\probmax_{i-1,j-1}(\len,\theta)$ that the segment goes from the reference tile to that with lower-left corner $(i-1,j-1)$ conditioned on $\theta$. The desired probability $\probmax(\len)$ will be obtained by averaging $\probmax_{i-1,j-1}(\len, \theta)$ with respect to $\theta$, summing over all $i, j \geq 1$ such that the tile with lower-left corner $(i-1, j-1)$ can be reached from the reference tile, and then using symmetry to take into account the tiles with $i \leq 0$ or $j \leq 0$.
